{\small Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices}

### 2017-11-13 Meetings/GPMNov2017/gpm_november2017_topic21.tex
Update to slides for GPM

  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1|only@1> AUG: All the shots were performed in the so-called
        Edge Optmized Configuration (EOC) shape. 
      \item<1|only@1> AUG: We matched correctly the shape and the L$_{\parallel}$
        here shown from outer divertor plate up to X-point 
      \item<2|only@2> AUG: The scan was performed with similar puffing
        rates for intermediate and higher current (0.8-1
        MA) whereas we reduced it at lower current to avoid early
        disruption
      \item<2|only@2> AUG: The total power (Ohmic plus NBI) was kept
        constant throughout the scan
      \item<2|only@2> AUG: We have comparable edge density, divertor neutral
        pressure and divertor temperature
      \item<3|only@3> TCV: We repeat the same excercise at TCV with a
        slight difference in the profile of parallel connection
        length. This required operation at unusual low toroidal field
        (up to 0.8T)
      \item<4|only@4> TCV: no additional heating
        has been used. Nevertheless the difference in power crossing the separatrix
        is small
      \item<4|only@4> TCV: The difference in target pressure similar
        to AUG behavior. 
      \item<5|only@5> AUG: At comparable edge density Upstream profiles are
        different with the tendency to develop shoulder easier at
        lower current. \alert{We have flattening of the upstream
          profiles only when $\Lambda_{div}$ is well above one on all
          the profile}
      \item<6|only@6> AUG: Neutrals estimated using calibrated D$_{\alpha}$
        cameras coupled with values of density and temperature at the
        target suggest a larger neutral density at lower current (even
        with comparable values of edge electron density)
      \item<7|only@7> AUG: At all the current a clear roll-over in
        peak density observed and we can also track the radiation
        front move away from target earlier in density at lower current
      \item<8|only@8> TCV: This tendency is not observed for TCV where
        profiles seem resilient to modification of Bt even though we
        reached pretty high value of $\Lambda_{div}$ all along the profile.
      \item<9|only@9> TCV: This is due to the fact that we can't
        observed during the density ramp any signature of rollover or detachment,
        \alert{whereas upstream profile modification at TCV are only observed
        well after rollover}
      \item<10|only@10> AUG: There is the tendency towards larger blobs
        at lower current at all values of $\Lambda_{div}$
      \item<11|only@11> AUG: This need to be further confirmed
        independently by GPI measurements (I. Cziegler \textit{et al.}). The present setup allows
        for space resolution of the order of mm with a 397 kframe/s
        sampling rate. Small amount of He gas flux needed ($\sim
        1.5e^{17} atoms/ms$)
      \item<12|only@12> TCV: this is not confirmed for TCV where blob
        sizes is rather constant over a rather large range of
        $\Lambda_{div}$. At the same time we do not observe target
        density rollover neither upstream profile flattening 
      \end{itemize}
    \end{column}
\end{columns}
\end{frame}

@@

  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1|only@1> AUG: We matched correctly the shape the parallel
        connection length L$_{\parallel}$ is modified consistently
      \item<1|only@1> AUG: The scan was performed with similar puffing rate (0.8-1
        MA) whereas we reduced it at lower current to avoid early disruption
      \item<2|only@2> AUG: We have comparable edge density and divertor neutral
        pressure even though pressure increase earlier at higher current
      \item<2|only@2> AUG: The total power (Ohmic plus NBI) was kept
        constant throughout the scan
      \item<3|only@3> TCV: We repeat the same excercise at TCV with a
        consistent variation of parallel connection length
      \item<4|only@4> TCV: no additional heating
        used. Nevertheless the difference in power crossing the separatrix
        is small
      \item<4|only@4> TCV: Neutral compression is roughly constant between
      \item<5|only@5> AUG: At comparable edge density Upstream profiles are
        different with the tendency to develop shoulder easier at
        lower current. \alert{We have flattening of the upstream
          profiles only when $\Lambda_{div}$ is well above one on all
          the profile}
        \item<6|only@6> Neutrals at lower current are substantially
          higher even with similar edge density profiles.
        \item<7|only@7> Neutrals at lower current are substantially
          higher even with similar edge density profiles.
      \item<8|only@8> TCV: This tendency is substantially confirmed at
        TCV where
        profiles  
      \item<9|only@9> TCV: This is consistent with onset of detachment
        (at least in intermediate and lower current)
      \item<10|only@10> AUG: While the general observation of increasing
        blob size with $\Lambda_{div}$ is confirmed there are no
        differences between the current
      \item<11|only@11> TCV: confirm the observation of AUG. 
      \end{itemize}
    \end{column}
\end{columns}
\end{frame}

>>>>

  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1|only@1> AUG: All the shots were performed in the so-called
        Edge Optmized Configuration (EOC) shape. 
      \item<1|only@1> AUG: We matched correctly the shape and the L$_{\parallel}$
        here shown from outer divertor plate up to X-point 
      \item<2|only@2> AUG: The scan was performed with similar puffing
        rates for intermediate and higher current (0.8-1
        MA) whereas we reduced it at lower current to avoid early
        disruption
      \item<2|only@2> AUG: The total power (Ohmic plus NBI) was kept
        constant throughout the scan
      \item<2|only@2> AUG: We have comparable edge density, divertor neutral
        pressure and divertor temperature
      \item<3|only@3> TCV: We repeat the same excercise at TCV with a
        slight difference in the profile of parallel connection
        length. This required operation at unusual low toroidal field
        (up to 0.8T)
      \item<4|only@4> TCV: no additional heating
        has been used. Nevertheless the difference in power crossing the separatrix
        is small
      \item<4|only@4> TCV: The difference in target pressure similar
        to AUG behavior. 
      \item<5|only@5> AUG: At comparable edge density Upstream profiles are
        different with the tendency to develop shoulder easier at
        lower current. \alert{We have flattening of the upstream
          profiles only when $\Lambda_{div}$ is well above one on all
          the profile}
      \item<6|only@6> AUG: Neutrals estimated using calibrated D$_{\alpha}$
        cameras coupled with values of density and temperature at the
        target suggest a larger neutral density at lower current (even
        with comparable values of edge electron density)
      \item<7|only@7> AUG: At all the current a clear roll-over in
        peak density at the target observed and we can also track the radiation
        front move away from target earlier in density at lower current
      \item<8|only@8> TCV: This tendency is not observed for TCV where
        profiles seem resilient to modification of Bt even though we
        reached pretty high value of $\Lambda_{div}$ all along the profile.
      \item<9|only@9> TCV: This is due to the fact that we can't
        observed during the density ramp any signature of rollover or detachment,
        \alert{whereas upstream profile modification at TCV are only observed
        well after rollover}
      \item<10|only@10> AUG: There is the tendency towards larger blobs
        at lower current at all values of $\Lambda_{div}$
      \item<11|only@11> AUG: This need to be further confirmed
        independently by GPI measurements (I. Cziegler \textit{et al.}). The present setup allows
        for space resolution of the order of mm with a 397 kframe/s
        sampling rate. Small amount of He gas flux needed ($\sim
        1.5e^{17} atoms/ms$)
      \item<12|only@12> TCV: this is not confirmed for TCV where blob
        sizes is rather constant over a rather large range of
        $\Lambda_{div}$. At the same time we do not observe target
        density rollover neither upstream profile flattening 
      \end{itemize}
    \end{column}
\end{columns}
\end{frame}

@@

  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1|only@1> AUG: We matched correctly the shape the parallel
        connection length L$_{\parallel}$ is modified consistently
      \item<1|only@1> AUG: The scan was performed with similar puffing rate (0.8-1
        MA) whereas we reduced it at lower current to avoid early disruption
      \item<2|only@2> AUG: We have comparable edge density and divertor neutral
        pressure even though pressure increase earlier at higher current
      \item<2|only@2> AUG: The total power (Ohmic plus NBI) was kept
        constant throughout the scan
      \item<3|only@3> TCV: We repeat the same excercise at TCV with a
        consistent variation of parallel connection length
      \item<4|only@4> TCV: no additional heating
        used. Nevertheless the difference in power crossing the separatrix
        is small
      \item<4|only@4> TCV: Neutral compression is roughly constant between
      \item<5|only@5> AUG: At comparable edge density Upstream profiles are
        different with the tendency to develop shoulder easier at
        lower current. \alert{We have flattening of the upstream
          profiles only when $\Lambda_{div}$ is well above one on all
          the profile}
        \item<6|only@6> AUG: Neutrals at lower current are substantially
          higher even with similar edge density profiles.
        \item<7|only@7> AUG: Similarly to the observation at constant
          q$_{95}$ target peak density rollover and radiation movement
          from the target occurs earlier in density at lower plasma current
      \item<8|only@8> TCV: This tendency is substantially confirmed at
        TCV where
        profiles  
      \item<9|only@9> TCV: This is consistent with onset of detachment
        (at least in intermediate and lower current)
      \item<10|only@10> AUG: While the general observation of increasing
        blob size with $\Lambda_{div}$ is confirmed there are no
        differences between the current
      \item<11|only@11> TCV: confirm the observation of AUG. 
      \end{itemize}
    \end{column}
\end{columns}
\end{frame}
